---
title: "Vis_1"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(tidyverse)
library(patchwork)
#library(rnoaa)
#remotes::install_github("ropensci/rnoaa", force = TRUE)
```

Import weather data

```{r, message = FALSE, warning = FALSE}
weather_df = read_csv("weather_df.csv")
weather_df = 
  mutate( weather_df,
    name = case_match(
      id, 
      "USW00094728" ~ "CentralPark_NY", 
      "USW00022534" ~ "Molokai_HI",
      "USS0023B17S" ~ "Waterhole_WA"), # creat new name variables.
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())

```

Make our first plot

```{r make plot, message = FALSE, warning = FALSE}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()

```

```{r makeplot, message = FALSE, warning = FALSE}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

```
```{r, message = FALSE, warning = FALSE}
ggp_weather_scatterplot = 
  weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

ggp_weather_scatterplot
```

Check why some rows are missing.
```{r, message = FALSE, warning = FALSE}
weather_df |> 
  filter(is.na(tmax))
```

## Fancier scatterplots!

```{r, message = FALSE, warning = FALSE}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) + # 3line
  geom_point(alpha = .3, size = .8) +
  geom_smooth(se = FALSE)
```

Where you define aesthetics can matter

```{r, message = FALSE, warning = FALSE}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = .3, size = .8) + # 1line
  geom_smooth(se = FALSE)
```

Use faceting real quick

```{r, message = FALSE, warning = FALSE}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name) # sep by name 
```

```{r, message = FALSE, warning = FALSE}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .3) + 
  geom_smooth(se = FALSE) +
  facet_grid(name ~ .) # sep by name 
```

Let's make a somewhat more interesting scatterplot!

```{r, message = FALSE, warning = FALSE}
weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name, size = prcp)) + # dif size of point
  geom_point(alpha = .3) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name) # sep by name 
```

```{r, message = FALSE, warning = FALSE}
weather_df |> 
  filter(name == "CentralPark_NY") |> 
  mutate(
    tmax_fahr = tmax * (9 / 5) + 32,
    tmin_fahr = tmin * (9 / 5) + 32
  ) |> 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm", se = FALSE)  
```

## Small things

```{r, message = FALSE, warning = FALSE}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  # geom_point(aes(color = name), alpha = .3, size = .8) +
  geom_smooth(se = FALSE)

```

```{r, message = FALSE, warning = FALSE}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
  #geom_hex(aes(color = name), alpha = .3, size = .8) +
  #geom_smooth(se = FALSE)
```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = "blue")) +
  geom_point()

weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(color = "blue") #right
```

## Univariable plots

```{r}
weather_df |> 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, colour = name )) +
  geom_histogram()

weather_df |> 
  ggplot(aes(x = tmin, fill = name )) +
  geom_histogram(position = "dodge")

```

How would i fix this? Maybe facet?

```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +
  facet_grid(. ~ name)

```

maybe a density plot?

```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3) +
  facet_grid(. ~ name)

```

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_boxplot(alpha = .3) +
  facet_grid(. ~ name)
```

Violin plot

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .3) 
```

ridge plot

```{r}
library(ggridges)
weather_df |> 
  ggplot(aes(x = tmin, y = name, fill = name)) +
  geom_density_ridges() 
```

LA univariate plots

```{r}
weather_df |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha = .3)

weather_df |> 
  ggplot(aes(x = name, y = prcp, fill = name)) +
  geom_boxplot(alpha = .3)

weather_df |> 
  filter(prcp > 10, prcp < 1000) |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha = .3)
```

## Saving and embedding plots

```{r}
ggp_weather = 
  weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point()

ggsave("ggp_weather.pdf", ggp_weather, width = 8, height = 6)
```
embedding plots

```{r, fig.width = 6, fig.asp = .6}
weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point()
```


